Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-08 manuscript.tex
8 updates

In this paper, we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF. This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN. In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.

>>>>

In this paper, a new approach for measuring shape changes in the CCF is proposed using the SN density to estimate the RV and shape of the CCF. 
This new method is compared to a commonly used method based on a Normal density fit to the CCF.  The mean of the Normal density is used as the estimated RV and the FWHM estimates the width of the CCF.  Because the Normal density does not have any skewness, another method is need to estimate the asymmetry of the CCF, and the BIS SPAN is often employed.
In addition, the proposed SN approach is compared to other parameterizations of the CCF asymmetry that have been shown to be sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
